---
title: "Reactivity"
output: html_document
runtime: shiny
---

# Shiny Reactivity

## Example with reactive Functions `textInput()` and `renderText()`:

```{r text-input, echo=FALSE}
textInput(inputId = "textInput",
          label = "Please enter some text:",
          value = "starting text")
```

```{r text-render, echo=FALSE}
renderText(input$textInput)
```



```{r date-input}
dateInput(inputId = "dateInput",
          label = "Select a date:")
```


# Naive Reactivity

## A `Date()` Object's internal representation is not user-friendly:

Internal representation (seconds since 01-Jan-1970):

```{r date-render}
renderText(input$dateInput)
```


## Make them more user-friendly using `lubridate` Functions:

```{r load-lubridate}
library(lubridate)
```


## Trying to store the `Date` Object ouside of a reactive Context fails:

```{r display-date, eval=FALSE}
theDate <- input$dateInput       # !!! NOT A REACTIVE CONTEXT !!!

renderText(
  sprintf(
    "%s %s, %s",
    month(theDate, label = TRUE, abbr = FALSE),
    day(theDate),
    year(theDate)
  )
)

```


# Correct Reactivity

## Using `reactive()` puts the Variable in a reactive Context:

```{r display-date2}
theDate <- reactive(input$dateInput)     # reactive context

renderText(
  sprintf(
    "%s %s, %s",         # "August 10, 2022"
    month(theDate(), label = TRUE, abbr = FALSE),
    day(theDate()),      # calling the reactive variable
    year(theDate())      # (in fact a function!)
  )
)

```


CAVE: The reactive variable requires to be called like a Function `theDate()`.

